A minimal reaction-diffusion neural model generates {\emph{C. elegans}} undulation

### 2020-05-18 paper.tex
Updates from Overleaf

\section{The FitzHugh-Nagumo Neuron}\label{sec: fhn}

In accord with the goal of this paper, we sought the simplest relevant neuronal model.  The classical Hodgkin-Huxley\cite{hodgkin1952} model of squid neurons has led to a variety of simpler conduction models, including the Morris-Lecar\cite{morris1981} and Fitzhugh-Nagumo models.

@@

\citet{nagumo1962} proposed a circuit to simulate a FitzHugh-Nagumo neuron, shown in \Fref{fig: nagumo_ckt}.  It used a tunnel diode to achieve a cubic-like activation function, and an inductor to integrate.  However, this approach presents several complications.  Tunnel diodes are rare, and rather expensive; inductors cannot be used in proximity because of mutual inductance effects, and are quite large.

\begin{figure}[h!]
    \centering
    \inputtikz{figures/nagumo/nagumo}
    \caption{The original circuit proposed by \citet{nagumo1962}.  Note the use of inductors for integration, and the tunnel diode to supply a cubic-like V-I curve.  Our circuit, based off \citet{keener1983}, is arranged in the same layout, to make the similarities and differences more explicit.}
    \label{fig: nagumo_ckt}
\end{figure}

\citet{keener1983} proposed a modified Nagumo circuit which used operational amplifiers ("op-amps") to achieve nonlinearity and create a piecewise linear function.  He used an op-amp under saturation to create a piecewise linear approximation to the cubic, which is sufficient to drive the FHN oscillator.  He also used an op-amp integrator to simulate an inductor.

As a result of the piecewise linear approximation to the cubic, the nullclines of the circuit system differ slightly from the original FitzHugh-Nagumo nullclines.  However, in experiments this did not cause any change in the dynamics of the individual neuron, or many connected together - the nullclines are sufficiently similar that the dynamics are effectively the same.

>>>>

\section{The FitzHugh-Nagumo Neuronal Model}\label{sec: fhn}

In accord with the goal of this paper, we sought the simplest relevant neuronal model.  The classical Hodgkin-Huxley\cite{hodgkin1952} model of squid neurons has led to a variety of simpler conduction models, including the Morris-Lecar\cite{morris1981} and Fitzhugh-Nagumo (FHN) models.

@@

\citet{nagumo1962} proposed a circuit to simulate a FitzHugh-Nagumo neuron, shown in \Fref{fig: nagumo_ckt}.  It used a tunnel diode to achieve a cubic-like activation function, and an inductor to differentiate the K current.  However, this approach presents several complications.  Tunnel diodes are rare, and rather expensive; inductors cannot be used in proximity because of mutual inductance effects, and are quite large.

\begin{figure}[h!]
    \centering
    \inputtikz{figures/nagumo/nagumo}
    \caption{The original circuit proposed by \citet{nagumo1962}.  Note the use of inductors for differentiation, and the tunnel diode to supply a cubic-like V-I curve.  Our circuit, based off \citet{keener1983}, is arranged in the same layout, to make the similarities and differences more explicit.}
    \label{fig: nagumo_ckt}
\end{figure}

\citet{keener1983} proposed a modified Nagumo circuit which used the saturation properties of operational amplifiers ("op-amps") to achieve cubic-like non-linearity in the FHN  model.He also used an op-amp and a capacitor to simulate the inductor in the original Nagumo circuit.

As a result of the piecewise linear approximation to the cubic, the nullclines of the circuit system differ slightly from the original FitzHugh-Nagumo nullclines.  However, in experiments this did not cause a significant change in the dynamics of the individual neuron, or many connected together - the nullclines are sufficiently similar that the dynamics are effectively the same.
